Reflections from reproductions

### 2024-08-15 pages/reflections.qmd
feat(reflections): add reflections from Kim et al. 2021

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 |

@@

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* <!-- TODO: Check run time of Huang -->
* @lim_staff_2020: Add parallel processing

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!----> | <!----> | ❌ |

@@

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ❌ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | <!----> | ❌ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | <!--TODO--> |

@@

@@

For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction.

>>>>

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ✅ | ✅ |

@@

@kim_modelling_2021: Provides commands to install packages required at the start of scripts, which I could then easily base renv on automatically (as it detects them).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | 🟡 |

@@

@kim_modelling_2021: States version of R but not package. Due to prior issues with backdating R, used latest versions. There were no issues using the latest versions of R and packages, but if there had been, it would be important to know what versions had previously been used and worked.

@@

* @shoaib_simulation_2021: Add parallel processing and ran fewer replications
* <!-- TODO: Check run time of Huang -->
* @lim_staff_2020: Add parallel processing
* @kim_modelling_2021: Reduced number of people in simulation, and switched from serial to the provided parallel option.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!----> | <!----> | ❌ | ❌ | N/A |

@@

@anagnostou_facs-charm_2022: Very quick! Seconds!

@@

<!--TODO: Figure where to put this... Kim et al. 2021: reproduction facilitated by provision of option to run model with parallel processing. However, would've been beneficial to provide suggestions for how to run model quicker on lower spec machine (e.g. lowering number of people) -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ❌ | ❌ |

@@

@kim_modelling_2021: Had to write code to find aorta sizes of people with AAA-related deaths.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | <!--TODO--> |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | <!--TODO--> | ❌ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | <!--TODO--> | ❌ |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ |

@@

For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction. For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create.

Fix errors in script. For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end.
